### 2017-03-28 ThesisText/experiments.tex
Corrects small details

Each object of the dataset contains information referencing a single student in
a single course. The objects contain the overall enrollment count and type of
student. They also contain the identification of a course along with the
semester and season of that course. Finally, the object contains a count of
CRUD activities of that student in that course.

@@

Table~\ref{tab:exp_002a_res} has a listing of objects that are placed in each
of the two clusters. It is observable that the major difference is in the
number of CRUD activities. Different values for activities remain the same for
different courses and enrollment numbers, but greater values are placed in one
cluster while lower values are placed in another.

@@

Each object of this dataset will have information on a single student. As
mentioned, an object has the number of enrolled and approved courses and the
sum of each CRUD activity for every course of that single student. Each entry
does not have the identification of the student to which it refers too because
that information is irrelevant for our learning objectives.

>>>>

Each object of the dataset contains information referencing a single student in
a single course. The objects contain the overall enrollment count and type of
student. They also contain the identification of a course along with the
semester and season of that course. Finally, the object contains a count
of~\gls{crud} activities of that student in that course.

@@

Table~\ref{tab:exp_002a_res} has a listing of objects that are placed in each
of the two clusters. It is observable that the major difference is in the
number of~\gls{crud} activities. Different values for activities remain the
same for different courses and enrollment numbers, but greater values are
placed in one cluster while lower values are placed in another.

@@

Each object of this dataset will have information on a single student. As
mentioned, an object has the number of enrolled and approved courses and the
sum of each~\gls{crud} activity for every course of that single student. Each
entry does not have the identification of the student to which it refers too
because that information is irrelevant for our learning objectives.

### 2017-03-28 ThesisText/statistics.tex
Corrects small details

The activity on a course is measured using the Moodle logs which contain the
CRUD activities. CRUD activities, as stated in~\ref{sec:logs}, are aggregated
by courses, students, and weeks. To have a sense of how activity changes over a
course we take the logs dataset and aggregate every object only by course. So,
each entry will have the sum of the activities aggregated by course and week.

@@

    \caption
        [Total number of activities vs mean of activities per week]
        {Total number of activities (right) vs total active courses (Left).}

>>>>

The activity on a course is measured using the Moodle logs which contain
the~\gls{crud} activities. \gls{crud} activities, as stated in~\ref{sec:logs},
are aggregated by courses, students, and weeks. To have a sense of how activity
changes over a course we take the logs dataset and aggregate every object only
by course. So, each entry will have the sum of the activities aggregated by
course and week.

@@

    \caption
        [Total number of active courses per week (bars) vs total active courses (Left)]
        {Total number of active courses per week (bars) vs total active courses (Left).}
